---
title: "Frequency Analysis"
author: "SA"
date: "8/14/2020"
output: html_document
---

```{r}
library(tidyverse)
library(data.table)
library(quanteda)
```

```{r}

maggie <- fread("maggie.csv")
#maggie <- fread("earphones.csv")
```

```{r}
library(dplyr)
library(tidyr)

#Assigning sentiments based on star ratings
maggie <- maggie %>% mutate(sentiment = case_when(stars < 3 ~ "Negative",
                                                  stars >3 ~ "Positive",
                                                  stars ==3 ~ "Neutral"))

maggi <- maggie %>% select(-c("stars", "comment"))

#Sentiment table
maggie_sentiment <- gather(maggi, key, sentiment, -date) %>% 
    count(date, key, sentiment) %>% 
    spread(sentiment, n, fill = 0)

maggie_sentiment <- maggie_sentiment %>% mutate(sum_sent = Negative + Positive + Neutral)
maggie_sentiment <- maggie_sentiment %>% mutate(Negative_shares = round((Negative/sum_sent)*100)) %>% 
  mutate(positive_share = round((Positive/sum_sent)*100)) %>% 
  mutate(neutral_share = round((Neutral/sum_sent)*100))
```


```{r}

maggie1 <- maggie %>% filter(date > "2019-12-31" & sentiment =="Negative") 
toks_text <- tokens(maggie$comment, remove_punct = TRUE) 

dfmat_text <- dfm(toks_text,tolower = TRUE, remove = c(stopwords("en"), "maggie", "pack", "product", "noodles", "2", "packs", "family", "regular","can", "maggi", "even", "really", "packets", "since", "just", "got", "within", "also", "ki", "kar", "if", "the", "good"))

tstat_freq <- textstat_frequency(dfmat_text, n = 40)

tstat_freq

textplot_wordcloud(dfmat_text, min_count = 10, max_words = 1000)



#Relative frequency analysis
tstat_key <- textstat_keyness(dfmat_text, 
                                target = maggie$sentiment == "Negative")


textplot_keyness(tstat_key) +
  theme_minimal() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())
```

#Collocation Analysis -- Nothing fun so far.
```{r}
tstat_col_caps <- tokens_select(toks_text, pattern = '^[A-Z]', 
                                valuetype = 'regex', 
                                case_insensitive = FALSE, 
                                padding = TRUE) %>% 
           textstat_collocations(min_count = 2)
tstat_col_caps
```

#add a new column -- sentiment-- to label stars >3 as positive, < 3 as negative and ==3 as neutral
```{r}

#maggie_sentiment <- maggie_sentiment %>% mutate(sent = apply(.[,3:5], 1, function(x) names(x)[which.max(x)]))
```

```{r}
library(ggplot2)


maggie_sentiment$date <- as.Date(maggie_sentiment$date)

maggi_long <- maggie_sentiment%>% select(-c("key", "Negative", "Neutral", "Positive", "sum_sent")) %>% filter(date > "2017-12-31")%>% gather("sentiment_share", "value",2:4)  # convert to long format

p <- ggplot(maggi_long,
       aes(x = date, y = value, colour = sentiment_share)) +
       geom_point(size = 0.2) +
       geom_smooth(method = lm) +
       scale_x_date(expand = c(0, 0), breaks = "2 month", minor_breaks = "4 week") + 
       ylab("share of reviews (%)") +
       xlab("") +
       scale_colour_brewer(palette = "Set1") + 
       theme_minimal() +
       theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_text(angle = 45))
  
p
ggsave("p1.jpeg")
```















